Rising from the Ashes: How the Milky Way Got Its Scars

### 2024-04-29 paper/sec/app.tex
Just, a ton of changes
Paper updates

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{mass_size.pdf}
  \caption{The mass and size evolution of the central (Milky Way, blue) and satellite (GSE, orange) galaxies. The mass is taken to be the stellar mass within twice the half-mass radius, and the size is taken to be the half-mass radius. In the upper panel, we also show as a horizontal line the mass of the Milky Way and GSE from the best-fit model of \citet{2021ApJ...923...92N}. This comparison is taken to be made at $3\,\Gyr$ (vertical dashed line), our proxy for $z\sim2$. A precise match is not attempted given the wide ranging uncertainties.}
  \label{fig:mass_size}
\end{figure}

@@

\section{Cause of Suppressed Star Formation}

>>>>

@@

\section{Cause of Suppressed Star Formation}\label{app:cause_qui}
